Open Science, Open Plant Pathology

### 2020-07-23 analysis/paper/paper.Rmd
Add Analysis section and update references

> "The closeness of agreement between independent results obtained with the same method on identical test material, under the same conditions (same operator, same apparatus, same laboratory and after short intervals of time). The measure of repeatability is the standard deviation qualified with the term: `repeatability' as repeatability standard deviation. In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability", [@mcnaught1997compendium].

@@

> "The closeness of agreement between independent results obtained with the same method on identical test material but under different conditions (different operators, different apparatus, different laboratories and/or after different intervals of time). The measure of reproducibility is the standard deviation qualified with the term 'reproducibility' as reproducibility standard deviation. In some contexts reproducibility may be defined as the value below which the absolute difference between two single test results on identical material obtained under the above conditions, may be expected to lie with a specified probability. Note that a complete statement of reproducibility requires specification of the experimental conditions which differ", [@mcnaught1997compendium].

@@

>>>>

> "The closeness of agreement between independent results obtained with the same method on identical test material, under the same conditions (same operator, same apparatus, same laboratory and after short intervals of time). The measure of repeatability is the standard deviation qualified with the term: `repeatability' as repeatability standard deviation. In some contexts repeatability may be defined as the value below which the absolute difference between two single test results obtained under the above conditions, may be expected to lie with a specified probability", [@McNaught1997].

@@

> "The closeness of agreement between independent results obtained with the same method on identical test material but under different conditions (different operators, different apparatus, different laboratories and/or after different intervals of time). The measure of reproducibility is the standard deviation qualified with the term 'reproducibility' as reproducibility standard deviation. In some contexts reproducibility may be defined as the value below which the absolute difference between two single test results on identical material obtained under the above conditions, may be expected to lie with a specified probability. Note that a complete statement of reproducibility requires specification of the experimental conditions which differ", [@McNaught1997].

@@

## Analysis

Bayesian mixed effect models were fit using the contributed package brms [@Burkner2018] in the R environment  [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

Relatively flat priors were selected with a mean 0 and a standard deviation 10 for the fixed effects.

The random effects were year and assignee for all models excepting the model which tested for year effects.
In this model the random effects were the publication title and assignee.

Models were fit using the `hurdle_gamma()` family function due to zero-inflated continuous data.
Each model was run for 3000 iterations in four chains.

The `adapt_delta()` and `max_treedepth()` values were adjusted as necessary on a case-by-case basis for each of the models to ensure that the chains mixed well.

Model finesses were evaluated using model summaries and diagnostic plots from brms [@Burkner2018] and posterior fits using `pp_check()` from the contributed R package bayesplot [@Gabry2019].

Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package bayestestR [@Makowski2019].
